\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx}  % \usepackage{times}
\input{header}

\setlength{\oddsidemargin}{0pt}
\setlength{\topmargin}{-.25in}	% technically should be 0pt for 1in
\setlength{\headsep}{3em}
\setlength{\textheight}{8.75in}
\setlength{\textwidth}{6.5in}
\setlength{\columnsep}{5mm}

% \markright{$\Upsilon$ \today \hfill}
% \pagestyle{myheadings}

\DoubleSpace

% -----------------------------------------------------------------------------

\begin{document}

\Heading{Answers to questions for a researcher: June 2009}

\section{Shape at a branch}

\begin{itemize}
\item 
What paper am I working on? Shape at a branch from contour-based points.
\item
Which conference will this paper go to? SIGGRAPH/SGP/MICCAI/CBMS/SMI.
\item 
What are the most relevant papers as background and competitive approaches?
\item
What papers am I reading? Bajaj/Barequet/Boissonnat/Christiansen
\item
What code am I writing? ctr08ToMeshDivideAndConquer.cpp
\item
What is the killer app for this research? anatomical modeling, 
                                          quantitative analysis of anatomy
\item
What is the cool demo for this research? rosette intermediate curve
\end{itemize}

\section{An input format for contours}

\begin{itemize}
\item 
What paper am I working on? Defining and parsing contour input.
\item
Which conference will this paper go to? tech report
\item 
What are the most relevant papers as background and competitive approaches?
Barequet; Meyers; Berkeley
\item
What papers am I reading? Teller on Berkeley format; compiler texts on parsing.
\item
What code am I writing? ctr08ToMesh(DivideAndConquer).cpp
\item
What is the killer app for this research? anatomical modeling
\item
What is the cool demo for this research?
\end{itemize}



\end{document}